\bf An Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems

### 2023-05-17 notes/tilingProject.tex
finalised the k space plots and videos of spin and pairing correlations

The following un-normalised combination of the auxiliary model eigenstates satisfies Bloch's theorem~\cite{stoyanova}:
\begin{equation}\begin{aligned}
	\ket{\Psi^n_{\vec k}} = \frac{1}{\mathcal{W} \sqrt N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
\end{aligned}\end{equation}
where \(N\) is the total number of lattice sites. The interpretation is that the set of \(n=0\) states form the lowest band in the spectrum of the lattice. Higher values of \(n\) produce the more energetic bands. The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\). We will actually work only in the lowest band \(n=0\), so we will drop the band index from now on and keep in mind that only the auxiliary model ground states appear in the formulation:
\begin{equation}\begin{aligned}
	\label{bloch-states}
	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
\end{aligned}\end{equation}
where \(\lambda_{\ket{\vec k}}\) is a normalisation factor.

@@

	\ket{\Psi_\text{gs}} = \frac{1}{\lambda_{\vec k_0} N}\sum_{\vec R_j, \vec a \in \text{NN of }\vec R_j} e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j, \vec a)}~,

@@

	\ket{\Psi_\text{gs}} = \sum_{\vec a \in \text{NN of}\vec R_0}\frac{1}{\mathcal{W}\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0, \vec a)} + \ket{\psi_\text{diff}(\vec k_0)}

@@

where \(\ket{\psi_\text{diff}(\vec k_0)} = \ket{\Psi_\text{gs}} - \frac{1}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k_0} N}\sum_{\vec R_j} \left[e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j)} - e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)}\right]\). The Greens funtion takes the form

@@

G_\text{H-H}(\vec r, t) =  \frac{-i\theta(t)}{\mathcal{W}^2 \lambda_{\vec k_0}^2}\sum_{\vec a_1, \vec a_2 \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a_1) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a_2)}~.

@@

	G_\text{loc}(t) \equiv G_\text{H-H}(\vec r=0, t) =  \frac{-i\theta(t)}{\mathcal{W}^2 \lambda_{\vec k_0}^2}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)}~.

@@

	G_\text{loc}(t) \equiv G_\text{H-H}(\vec r=0, t) &= -\frac{1}{\mathcal{W}\lambda_{\vec k_0}^2 }i\theta(t) \braket{\psi_\text{aux}(\vec R_0) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0)}~.

@@

For the nearest neighbour Greens function \(G_\text{H-H}(\vec r=\vec a, t)\), we keep only the terms with \(\vec a_1 = \vec a_2 = \vec a\) in the summation of eq.~\ref{greens_func_approx}:
\begin{equation}\begin{aligned}
	G_\text{H-H}(\vec r=\vec a, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}^2}i\theta(t) \braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + \vec a)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)} = \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}^2} \mathcal{G}_{dz}(t)~.
\end{aligned}\end{equation}

@@

\section{Static correlation functions}
This approach also holds for higher-order static correlation functions. For example, a general local correlation of the form \(\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}}\) corresponding to operators \(\mathcal{O}_1\) and \(\mathcal{O}_2\) can be estimated, using this method, in terms of auxiliary model quantities. For that, we first express the correlation at sites \(\vec R_0\) as well as its nearest neighbours: 
\begin{equation}\begin{aligned}
	\frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} + \frac{1}{\mathcal{W}}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + \vec a) | \Psi_\text{gs}}\right]
\end{aligned}\end{equation}
This is enabled by the translation symmetry of the problem, and it allows us to involve both the impurity site and the bath zeroth site in the relations. By keeping only the uniform part of the ground-state wavefunction, we get
\begin{equation}\begin{aligned}
	\label{local_correlation}
	\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} \simeq& \frac{1}{2\lambda_{\vec k_0}^2}\left[\frac{1}{\mathcal{W} }\braket{\psi_\text{aux}(\vec R_0) | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \psi_\text{aux}(\vec R_0)} \right. \\
													   &+ \left.\frac{1}{\mathcal{W}^3}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + \vec a) | \psi_\text{aux}(\vec R_0, \vec a)}\right]\\
	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]
\end{aligned}\end{equation}
In the above expression, where the arguments \((d)\) and \((z)\) indicate that the corresponding operator acts at the impurity site and the bath zeroth site respectively, and the subscript \(\text{aux}\) indicates that the averaging is carried out in the impurity model.

Similar expressions hold for non-local correlation functions.
\begin{equation}\begin{aligned}
	\label{nonlocal_correlation}
	&\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) | \Psi_\text{gs}} \\
	=& \frac{1}{4}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) + \mathcal{O}_1(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \Psi_\text{gs}}\right]\\
	\simeq& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) | \psi_\text{aux}(\vec R_0, \vec a)} \right. \\
	      &\left.\braket{\psi_\text{aux}(\vec R_0, -\vec a) | \mathcal{O}_1(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \psi_\text{aux}(\vec R_0, -\vec a)}\right]\\
	=& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right]
\end{aligned}\end{equation}
In the first equation, the first two terms were introduced to incorporate effects arisingfrom the bath zeroth and first sites (guided by the dynamics of the transition in the underlying extended Anderson model), while the last two terms were introduced to symmetrise the effects of choosing \(\vec R_0\) as \(d\) and \(\vec R_0 + \vec a\) as \(z\), and not other way round. The argument \((1)\) in the operators indicate that theu act at the first site of the bath (beyond the bath zeroth site).

The next-nearest correlation function is relatively simpler, becuase only those terms contribute that involve both the impurity as well as the first site. If \(\vec a^\prime\) denotes the relative vector between a given site and one of its next-nearest neighbours, we can write
\begin{equation}\begin{aligned}
	\label{nnn_correlation}
	\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) | \Psi_\text{gs}} =& \frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) + \mathcal{O}_1(\vec R_0 - \vec a^\prime) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}}\right]\\
	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right]
\end{aligned}\end{equation}

@@

	\rho_{\vec k,\sigma} =& \sum_{n_{(d,z,1),\sigma}=0,1}\frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{d\sigma}} + \frac{1}{\mathcal{W}}|\alpha_{n_{z\sigma}}|^2\right]\\

>>>>

The following un-normalised combination of the auxiliary model eigenstates satisfies Bloch's theorem~\cite{stoyanova}:
\begin{equation}\begin{aligned}
	\ket{\Psi^n_{\vec k}} = \frac{1}{\sqrt{\mathcal{W} N}}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
\end{aligned}\end{equation}
where \(N\) is the total number of lattice sites. The interpretation is that the set of \(n=0\) states form the lowest band in the spectrum of the lattice. Higher values of \(n\) produce the more energetic bands. The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\). We will actually work only in the lowest band \(n=0\), so we will drop the band index from now on and keep in mind that only the auxiliary model ground states appear in the formulation:
\begin{equation}\begin{aligned}
	\label{bloch-states}
	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} \sqrt{\mathcal{W} N}}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
\end{aligned}\end{equation}
where \(\lambda_{\ket{\vec k}}\) is a normalisation factor.

@@

	\ket{\Psi_\text{gs}} = \frac{1}{\lambda_{\vec k_0} \sqrt{\mathcal{W} N}}\sum_{\vec R_j, \vec a \in \text{NN of }\vec R_j} e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j, \vec a)}~,

@@

	\ket{\Psi_\text{gs}} = \sum_{\vec a \in \text{NN of}\vec R_0}\frac{1}{\sqrt \mathcal{W}\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0, \vec a)} + \ket{\psi_\text{diff}(\vec k_0)}

@@

where \(\ket{\psi_\text{diff}(\vec k_0)} = \ket{\Psi_\text{gs}} - \frac{\sqrt \mathcal{W}}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)}\). The Greens funtion takes the form

@@

G_\text{H-H}(\vec r, t) =  \frac{-i\theta(t)}{\mathcal{W} \lambda_{\vec k_0}^2}\sum_{\vec a_1, \vec a_2 \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a_1) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a_2)}~.

@@

	G_\text{loc}(t) \equiv G_\text{H-H}(\vec r=0, t) =  \frac{-i\theta(t)}{\mathcal{W} \lambda_{\vec k_0}^2}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)}~.

@@

	G_\text{loc}(t) \equiv G_\text{H-H}(\vec r=0, t) &= -\frac{1}{\lambda_{\vec k_0}^2 }i\theta(t) \braket{\psi_\text{aux}(\vec R_0) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0)}~.

@@

For the nearest neighbour Greens function \(G_\text{H-H}(\vec r=\vec a, t)\), we keep only the terms with \(\vec a_1 = \vec a_2 = \vec a\) in the summation of eq.~\ref{greens_func_approx}:
\begin{equation}\begin{aligned}
	G_\text{H-H}(\vec r=\vec a, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}}i\theta(t) \braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + \vec a)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)} = \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}} \mathcal{G}_{dz}(t)~.
\end{aligned}\end{equation}

@@

\section{Static correlation functions}
This approach also holds for higher-order static correlation functions. For example, a general local correlation of the form \(\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}}\) corresponding to operators \(\mathcal{O}_1\) and \(\mathcal{O}_2\) can be estimated, using this method, in terms of auxiliary model quantities. For that, we first express the correlation at sites \(\vec R_0\) as well as its nearest neighbours: 
\begin{equation}\begin{aligned}
	\frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} + \frac{1}{\mathcal{W}}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + \vec a) | \Psi_\text{gs}}\right]
\end{aligned}\end{equation}
This is enabled by the translation symmetry of the problem, and it allows us to involve both the impurity site and the bath zeroth site in the relations. By keeping only the uniform part of the ground-state wavefunction, we get
\begin{equation}\begin{aligned}
	\label{local_correlation}
	\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} \simeq& \frac{1}{2\lambda_{\vec k_0}^2}\left[\frac{1}{\mathcal{W} }\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0, \vec a) \mathcal{O}_2(\vec R_0) | \psi_\text{aux}(\vec R_0)} \right. \\
													   &+ \left.\frac{1}{\mathcal{W}^2}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + \vec a) | \psi_\text{aux}(\vec R_0, \vec a)}\right]\\
	=& \frac{1}{2\lambda_{\vec k_0}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]
\end{aligned}\end{equation}
In the above expression, where the arguments \((d)\) and \((z)\) indicate that the corresponding operator acts at the impurity site and the bath zeroth site respectively, and the subscript \(\text{aux}\) indicates that the averaging is carried out in the impurity model.

Similar expressions hold for non-local correlation functions.
\begin{equation}\begin{aligned}
	\label{nonlocal_correlation}
	&\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) | \Psi_\text{gs}} \\
	=& \frac{1}{4}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) + \mathcal{O}_1(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \Psi_\text{gs}}\right]\\
	\simeq& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) | \psi_\text{aux}(\vec R_0, \vec a)} \right. \\
	      &\left.\braket{\psi_\text{aux}(\vec R_0, -\vec a) | \mathcal{O}_1(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \psi_\text{aux}(\vec R_0, -\vec a)}\right]\\
	=& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right]
\end{aligned}\end{equation}
In the first equation, the first two terms were introduced to incorporate effects arisingfrom the bath zeroth and first sites (guided by the dynamics of the transition in the underlying extended Anderson model), while the last two terms were introduced to symmetrise the effects of choosing \(\vec R_0\) as \(d\) and \(\vec R_0 + \vec a\) as \(z\), and not other way round. The argument \((1)\) in the operators indicate that theu act at the first site of the bath (beyond the bath zeroth site).

The next-nearest correlation function is relatively simpler, becuase only those terms contribute that involve both the impurity as well as the first site. If \(\vec a^\prime\) denotes the relative vector between a given site and one of its next-nearest neighbours, we can write
\begin{equation}\begin{aligned}
	\label{nnn_correlation}
	\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) | \Psi_\text{gs}} =& \frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) + \mathcal{O}_1(\vec R_0 - \vec a^\prime) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}}\right]\\
	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right]
\end{aligned}\end{equation}

@@

	\rho_{\vec k,\sigma} =& \sum_{n_{(d,z,1),\sigma}=0,1}\frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{d\sigma}} + \frac{1}{\mathcal{W}}\bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{z\sigma}}\right]\\
